Many Analystis Project

### 2021-09-28 analysis.Rmd
Update analysis.Rmd

@@

```{r}
wb1 <- wbpsych %>%
  ggplot(aes(
    x = country,
    y = wb_psychANXIETY,
    group = country,
    color = country
  )) +
  geom_boxplot(notch = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  geom_point(position = "jitter", alpha = .1) +
  ggtitle("Importance Believe in God") +
  ylab("") + 
  theme(axis.text.x = element_text(angle = 30))
wb1

@@

Religion correlations

```{r, cache = TRUE}
rel %>%
  correlation( partial = FALSE, multilevel = TRUE ) %>%
  plot() + theme_blackboard()
```

General well-being correlations

```{r cache = TRUE}
wbgen %>%
  correlation( partial = FALSE, multilevel = TRUE ) %>%
  plot() + theme_blackboard()
```

Physical well-being correlations

```{r}
wbphys %>%
  correlation( partial = FALSE, multilevel = TRUE ) %>%
  summary()

wbphys %>%
  correlation( partial = FALSE, multilevel = TRUE ) %>%
  plot() + theme_blackboard()
```

Psychological well-being correlations

```{r}
wbpsych %>%
  select(-wb_psychMEANING)%>%
  correlation( partial = FALSE, multilevel = TRUE ) %>%
  summary()

wbpsych %>%
  select(-wb_psychMEANING)%>%
  correlation( partial = FALSE, multilevel = TRUE ) %>%
  plot()  + theme_abyss()
```

>>>>

```{r, cache = TRUE}
library(viridis)
p0 <- brms::conditional_effects(
  m2o,
  "bg_s",
  spaghetti = T,
  categorical = TRUE,
  ndraws = 200,
  prob = .89,
  method = 'posterior_epred'
)

@@

```{r}
wbpsych
wb1 <- wbpsych %>%
  ggplot(aes(
    x = country,
    y = 6 - wb_psychANXIETY, # reverse code
    group = country,
    color = country
  )) +
  geom_boxplot(notch = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  geom_point(position = "jitter", alpha = .1) +
  ggtitle("Importance Believe in God") +
  ylab("") + 
  theme(axis.text.x = element_text(angle = 30))
wb1

@@

<!-- Religion correlations -->

<!-- ```{r, cache = TRUE} -->
<!-- rel %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot() + theme_blackboard() -->
<!-- ``` -->

<!-- General well-being correlations -->

<!-- ```{r cache = TRUE} -->
<!-- wbgen %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot() + theme_blackboard() -->
<!-- ``` -->

<!-- Physical well-being correlations -->

<!-- ```{r} -->
<!-- wbphys %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   summary() -->

<!-- wbphys %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot() + theme_blackboard() -->
<!-- ``` -->

<!-- Psychological well-being correlations -->

<!-- ```{r} -->
<!-- wbpsych %>% -->
<!--   select(-wb_psychMEANING)%>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   summary() -->

<!-- wbpsych %>% -->
<!--   select(-wb_psychMEANING)%>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot()  + theme_abyss() -->
<!-- ``` -->
